Interest Flooding Attack and Countermeasures in Named Data Networking

### 2013-01-15 05-evaluation.tex
typos
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@939 df1a90cd-247b-4364-bdaf-287a704eb499

% Traffic pattern
In our experiments, we assume that legitimate users express Interests at constant average rates with randomized time gap between two consecutive Interests, where the random number for the gap follows a uniform distribution. We believe that this traffic pattern provides a reasonable approximation of traffic mix from all network users without excessive buffering. To quantify the behavior of our mitigation strategies under a worse case attack scenario, we assume all the attackers send junk Interests as fast as they can, no Interest --including legitimate ones-- can be satisfied from caches, routers are configured for single-path routing and there is only one, single-homed producer for the prefix under attack.
%(remember, that Interest limits will not allow real flooding of Intersests in all of the designed mitigation algorithms).

@@

Our next goal is to study the effectiveness of our mitigation algorithms as a function of increasing adversaries in the network.
To this end, we vary the percentage of attackers in the topology from 6\% to over 50\%. Since the total number of end users in the topology is constant, as the number of attackers increases, the number of legitimate users decreases. All other parameters and experimental set-up is the same with the previous experiment. As before, for each mitigation algorithm, we perform 10 independent simulation runs.
%The second set of conducted experiments was aimed to answer the question of the effect and quality of the Interest flooding attack mitigation algorithm under different attack volume.
%To do this, for each algorithm we varied the number of adversary nodes in the topology, keeping the total number of client nodes constant: 1 attacker and 15 legitimate users, 3 attackers and 13 legitimate users, etc.

@@

\begin{figure}[htbp]
  \centering
  \vspace{-.1cm}\includegraphics[scale=0.15,angle=90,height=3.5cm,width=8cm]{7018-r0}
  \caption{Internet-like topology: 344 client routers (red), 109 gateway routers (green), 109 backbone routers (blue)}\vspace{-.2cm}
  \label{fig:large-scale-topo}
\end{figure}

\begin{table}[htbp]
\centering
\caption{Large-scale topology link bandwidth and delay ranges}
\label{tab:large-scale}
\begin{tabular}{|l||c|c||c|c|}
  \hline
  \multirow{2}{*}{\bf Link type} &  \multicolumn{2}{|c||}{\bf Delay} &  \multicolumn{2}{|c|}{\bf Bandwidth} \tabularnewline
  \cline{2-5}
                        &  Min & Max                       &  Min & Max \tabularnewline
  \hline \hline
  Backbone--Backbone    & 5~ms & 10~ms   & 40~Mbps & 100~Mbps \tabularnewline
  \hline
  Gateway--Backbone,    & \multirow{2}{*}{5~ms} & \multirow{2}{*}{10~ms}   
                        & \multirow{2}{*}{10~Mbps} & \multirow{2}{*}{20~Mbps} \tabularnewline
  Gateway--Gateway      & & & & \\
  \hline
  Client--Gateway       & 10~ms & 70~ms   & 1~Mbps  & 3~Mbps \\
  \hline

\end{tabular}
\end{table}

@@

\begin{figure}[tbh]
 \centering
 \includegraphics[scale=0.8]{paper-topo-7018-gw/7018-r0-good-0-producer-gw}
 \vspace{-.3cm}\caption{Satisfaction ratio dynamics during the attack for large-scale topology with 40\% attackers)}\vspace{-.4cm}
 % producer on a gateway node
 \label{fig:large-scale}
\end{figure}

@@

All our evaluations leaves us with the conclusion that, among the three techniques we tested under various topology and attacker concentrations, the satisfaction-based pushback is the most effective one in mitigating interest flooding attacks.% and it restricts malicious Interests from even entering the network. 
%The only short periods of time when malicious Interests are getting admitted to the network is when routers have either no prior knowledge about per-interface satisfaction ratios (the initial period of the attack) or such knowledge becomes stale (statistics decaying during the attack). As soon as the knowledge is obtained or refreshed, the service for legitimate users returns to norm.

@@

This paper is a first step in understanding the impact of Interest flooding attacks in NDN and exploring the solution space. 
While designing our mitigation algorithms, we exploit two key features of NDN architecture, namely routers maintaining state about the Interests they have forwarded and Data traffic taking the reverse path of the Interest traffic. 
We test the efficacy of our algorithms by simulating them on both a simple binary-tree topology % designed to test the worst-case effectiveness of our algorithms as well as on a realizing 
as well as a more realistic ISP-based topology designed to provide insights of our algorithms' behavior when deployed on a real network. 
While our results are promising and show a great potential in mitigating Interest flooding DDoS attacks, there are certain limitations which should be addressed in future research.

>>>>

% Traffic pattern
In our experiments, we assumed that legitimate users express Interests at constant average rates with randomized time gap between two consecutive Interests, where the random number for the gap follows a uniform distribution. We believe that this traffic pattern provides a reasonable approximation of traffic mix from all network users without excessive buffering. To quantify the behavior of our mitigation strategies under a worse case attack scenario, we assumed that all the attackers send junk Interests as fast as they can, no Interest---including legitimate ones---can be satisfied from caches.  Also, we configured routers for single-path Interest forwarding and there is only one single-homed producer for the prefix under attack.
%(remember, that Interest limits will not allow real flooding of Intersests in all of the designed mitigation algorithms).

@@

Our next goal is to study the effectiveness of our mitigation algorithms as a function of increasing adversaries in the network.
To this end, we vary the percentage of attackers in the topology from 6\% to over 50\%. Since the total number of end users in the topology is constant, as the number of attackers increases, the number of legitimate users decreases. All other parameters and experimental setup is the same with the previous experiment. As before, for each mitigation algorithm, we perform 10 independent simulation runs.
%The second set of conducted experiments was aimed to answer the question of the effect and quality of the Interest flooding attack mitigation algorithm under different attack volume.
%To do this, for each algorithm we varied the number of adversary nodes in the topology, keeping the total number of client nodes constant: 1 attacker and 15 legitimate users, 3 attackers and 13 legitimate users, etc.

@@

\begin{figure}[htbp]
  \centering
  \vspace{-.1cm}\includegraphics[scale=0.15,angle=90,height=3.5cm,width=8cm]{7018-r0}
  \vspace{-0.3cm}
  \caption{Internet-like topology: 344 client routers (red), 109 gateway routers (green), 109 backbone routers (blue)}\vspace{-.2cm}
  \label{fig:large-scale-topo}
\end{figure}

\begin{table}[htbp]
\centering
\caption{Large-scale topology link bandwidth and delay ranges}
\vspace{-0.3cm}
\label{tab:large-scale}
\begin{tabular}{|l||c|c||c|c|}
  \hline
  \multirow{2}{*}{\bf Link type} &  \multicolumn{2}{|c||}{\bf Delay} &  \multicolumn{2}{|c|}{\bf Bandwidth} \tabularnewline
  \cline{2-5}
                        &  Min & Max                       &  Min & Max \tabularnewline
  \hline \hline
  Backbone--Backbone    & 5~ms & 10~ms   & 40~Mbps & 100~Mbps \tabularnewline
  \hline
  Gateway--Backbone,    & \multirow{2}{*}{5~ms} & \multirow{2}{*}{10~ms}   
                        & \multirow{2}{*}{10~Mbps} & \multirow{2}{*}{20~Mbps} \tabularnewline
  Gateway--Gateway      & & & & \\
  \hline
  Client--Gateway       & 10~ms & 70~ms   & 1~Mbps  & 3~Mbps \\
  \hline
\end{tabular}
\vspace{-0.3cm}
\end{table}

@@

\begin{figure}[tbh]
 \centering
 \includegraphics[scale=0.8]{paper-topo-7018-gw/7018-r0-good-0-producer-gw}
 \vspace{-.3cm}\caption{Satisfaction ratio dynamics during the attack for large-scale topology with 40\% attackers)}\vspace{-.3cm}
 % producer on a gateway node
 \label{fig:large-scale}
\end{figure}

@@

All our evaluations leaves us with the conclusion that, among the three techniques we tested under various topology and attacker concentrations, the satisfaction-based pushback is the most effective one in mitigating Interest flooding attacks.% and it restricts malicious Interests from even entering the network. 
%The only short periods of time when malicious Interests are getting admitted to the network is when routers have either no prior knowledge about per-interface satisfaction ratios (the initial period of the attack) or such knowledge becomes stale (statistics decaying during the attack). As soon as the knowledge is obtained or refreshed, the service for legitimate users returns to norm.

@@

This paper is a first step in understanding the impact of Interest flooding attacks in NDN and exploring the solution space. 
While designing our mitigation algorithms, we exploit two key features of NDN architecture, namely routers maintaining state about the Interests they have forwarded and Data traffic taking the reverse path of the Interest traffic. 
We test the efficacy of our algorithms by simulating them on both a simple binary-tree topology, % designed to test the worst-case effectiveness of our algorithms as well as on a realizing 
as well as a more realistic ISP-based topology designed to provide insights of our algorithms' behavior when deployed on a real network. 
While our results are promising and show a great potential in mitigating Interest flooding DDoS attacks, there are certain limitations which should be addressed in future research.
